Trends of SDR in Thessaloniki

### 2023-06-30 Article.Rmd
Commit 2023-06-30 21:17

There is a consensus, among researchers, that the major factors of the attenuation of SDR is the interaction with the atmospheric aerosols and the clouds. 
Those interactions, among other factors, have been analysed with modeling [@Li2016; @Samset2018], showing the existence of feedback mechanisms between the two.
And similar finds, have been showed in observational data [@Schwarz2020; @Ohvril2009; @Zerefos2009; @Xia2007 and references therein].

<!-- Sun variability: should cite that there is no significant trend found Wild2021 -->

@@

Due to the variability of those factors and the interaction between them,

@@

it is difficult to estimate the SDR trends on each site.

There is a also a need to evaluate the trends on different location

In this study, we examine the trends of SDR with ground-based measurements at Thessaloniki for the period 1993 - 2023, as derived from a CM-21 pyranometer.
<!-- goals -->
We reevaluate and extend the dataset used by @Bais2013, applying a different algorithm for the identification of clear-/cloud-sky instances, and we derive the radiation trends for this period under different sky conditions (all-sky, clear-sky and cloud-sky).

@@

<!-- CS_id v14.2 inserted here -->
```{r setup, echo=F, include=T, eval=TRUE}
## Load Clear Sky id variables
MS <- data.frame(readRDS("~/CS_id/PARAMS/Clear_sky_id_Reno-Hansen_apply_v14_2.Rds"))
# export all variables
for (an in names(MS)) {
    assign(an, MS[[an]])
}
```

>>>>

There is a consensus, among researchers, that the major factors of the attenuation of SDR is the interaction with the atmospheric aerosols and the clouds. 
Those interactions, among other factors, have been analysed with modeling [@Li2016; @Samset2018], showing the existence of feedback mechanisms between the two.
Similar finds, have been showed in observational data [@Schwarz2020; @Ohvril2009; @Zerefos2009; @Xia2007 and references therein].
<!-- Sun variability: should cite that there is no significant trend found Wild2021 -->

Due to the variability of the phenomenon, and its contributing factors, there is a need to further investigate SDR tendencies, in different sites, to estimate its magnitude, and its relation to the local conditions.
In this study, we examine the trends of SDR, with ground-based measurements at Thessaloniki for the period 1993 - 2023, as derived from a CM-21 pyranometer.
<!-- goals -->
We reevaluated and extended the dataset used by @Bais2013, applying a different algorithm for the identification of clear-/cloud-sky instances [@Reno2016; @Reno2012a], and we derive the radiation trends for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, under different sky conditions (all-sky, clear-sky and cloud-sky).

@@

@@

@@

```{r setup, echo=F, include=T, eval=TRUE}
## Load Clear Sky id v14.2 variables
MS <- data.frame(readRDS("~/CS_id/PARAMS/Clear_sky_id_Reno-Hansen_apply_v14_2.Rds"))
# export all Clear Sky variables
for (an in names(MS)) {
    assign(an, MS[[an]])
}
## get TSI slope for reference
TSI <- data.table(read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE))
TSI <- TSI[grep("TSI", TSI$var), ]
TSI$slope.sd           <- NULL
TSI$slope.ConfInt_0.95 <- NULL
TSI$slope.ConfInt_0.99 <- NULL
TSI$var                <- NULL
setorder(TSI, -slope.stat_sig)
rownames(TSI) <- NULL
names(TSI) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
TSIskopeAll <- TSI[`Sky condition` == "All sky cond."]
```
